---
title: "Exam"
author: "Lucas Vicentim Perasolo"
date: "31/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Dependencies
```{r, message=FALSE}
library(openintro)
library(tidyverse)
library(GGally)
library(infer)
library(ggplot2)
library(ggfortify)

```

#### FundamentalsÇ reading data
```{r}
tests <- read_csv("test_data.csv")
tests %>% 
      group_by(group) %>%
      summarise(mean = mean(EeDbY)) %>%
      slice(1)

```



#### Sheet 2: Read Data, Mean & Median Analysis, Boxplot and Association between Variables
```{r, message=FALSE}
acs12 %>%
  group_by(race) %>%
    summarise(sample_mean = mean(time_to_work, na.rm = TRUE),
              sample_median = median(time_to_work, na.rm = TRUE))
```

Plotting the relationship between a discrete x and continuos y
```{r}
ggplot(acs12, aes(x=race, y=time_to_work)) + geom_boxplot()
```

Plotting the relationship between a continuos y and continuos y
```{r}
ggplot(acs12, aes(x=time_to_work, y=income)) + geom_point()
quantile(acs12$income, .95, na.rm = TRUE)

```

#### Sheet 3: Import data, Group, Mean/Median/SD/Max/Total number anlayzis, Contigency table, Probability

Importing data and plotting
```{r, message=FALSE}
covid_data <- read_csv("covid.csv")

date_total <- covid_data %>%
                group_by(date) %>%
                summarise(total_infected = sum(number_infected, na.rm=TRUE))
ggplot(date_total, aes(x=date, y=total_infected)) + geom_line()

```

Grouping data by a parameter which first must be created becuase it depends on the sum of values from another parameter
```{r,  message=FALSE}
federal_average <- covid_data %>%
                    group_by(federal_state) %>%
                    summarise(average_infection = mean(number_infected))
federal_average
```

Analyzing according to a specific filter
```{r, message=FALSE}
bayern <- covid_data %>%
            filter(federal_state == "Bayern") %>%
            group_by(date) %>%
            summarise(total_infected_bayern_date = sum(number_infected, na.rm=TRUE)) %>%
            summarise(mean = mean(total_infected_bayern_date),
                             median = median(total_infected_bayern_date),
                             std = sd(total_infected_bayern_date),
                             max = max(total_infected_bayern_date),
                             total = sum(total_infected_bayern_date), na.rm=TRUE)
```

Contigency table
```{r, message=FALSE}
c_table <- read_csv("covid_too.csv")

dt <- table(c_table$sex, c_table$age_group)
addmargins(dt)

```

#### Sheet 4: Randomization technique (Checking for independence)

H0 : The variables group and survived are independent. They have no relationship, and the difference in survival
rates between the control and treatment groups was due to chance. In other words, heart transplant is not effective.
and hence evidence in favour of the alternative hypothesis

HA : The variables group and survived are not independent. The difference in survival rates between the control and
treatment groups was not due to chance and the heart transplant is effective

Preparing
```{r}
df <- tibble(
transplant = c(rep('treatment', 69), rep('control', 34)),
survived = c(rep(c('yes', 'no'), c(24, 45)),
rep(c('yes', 'no'), c(4, 30)))
)

(treatment_per <- df %>%
filter(transplant == 'treatment', survived == 'yes') %>%
summarise(per_surv = n() / nrow(filter(df, transplant == 'treatment'))))

(control_per <- df %>%
filter(transplant == 'control', survived == 'yes') %>%
summarise(per_surv = n() / nrow(filter(df, transplant == 'control'))))

(diff_stat <- treatment_per - control_per)
```

Idea: Randomly permute the variable transplant and leave survived as it is. If they are independent,
the value of the statistic should be comparable. But we need to repeat those steps several times.

```{r, message=FALSE}
set.seed(12345) # running this command, makes the result reproducible
N <- 100
diff_stat_perm <- vector("numeric", N)
for(i in 1:N){
df_perm <- df %>%
mutate(transplant = sample(transplant, nrow(df)))
df_perm_perc <- df_perm %>%
group_by(transplant, survived) %>%
summarise(n = n()) %>%
mutate(freq = n / sum(n))
diff_stat_perm[i] <- df_perm_perc$freq[4] - df_perm_perc$freq[2]
}
sum(abs(diff_stat_perm) >= diff_stat) / N

```
This means, that we observed a difference (in absolute value) as least as large as 0.230179028132992 just in 0.01 of
the N=100 simulation runs.
The data provide convincing evidence for the alternative hypothesis of dependence between the variables transplant
and survived. Hence there is convincing evidence to suggest that the transplant program is effective.

#### Sheet 05 Distributions

##### Normal Distribution functions 
```{r}
# NORMAL DISTRIBUTION

#dnorm(x, mean = 0, sd = 1, log = FALSE)
#pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE) -> Normal probabilities (!)
#qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE) -> Quantiles (!)
#rnorm(n, mean = 0, sd = 1)
 
ggplot(data.frame(x = c(-5, 5)), aes(x)) + stat_function(fun = dnorm) + theme_bw() + ylab("f(x)") + ggtitle(expression(paste(mu,"= 55","and", sigma, "=6")))
pert <- pnorm(54, mean=55, sd =6)
pert

# BINOMIAL DISTRIBUTION 

#dbinom(x, size, prob, log = FALSE)
#pbinom(q, size, prob, lower.tail = TRUE, log.p = FALSE) -> Binomial probability (!)
#qbinom(p, size, prob, lower.tail = TRUE, log.p = FALSE) -> Quantiles (!)
#rbinom(n, size, prob) 

# NEGATIVE BINOMIAL DISTRIBUTION 

#dnbinom(x, size, prob, mu, log = FALSE)
#pnbinom(q, size, prob, mu, lower.tail = TRUE, log.p = FALSE) -> Negative Binomial probability (!)
#qnbinom(p, size, prob, mu, lower.tail = TRUE, log.p = FALSE) -> Quantiles 
#rnbinom(n, size, prob, mu)

# GEOMETRIC DISTRIBUTIONS 

#dgeom(x, prob, log = FALSE)
#pgeom(q, prob, lower.tail = TRUE, log.p = FALSE)
#qgeom(p, prob, lower.tail = TRUE, log.p = FALSE)
#rgeom(n, prob)

```


#### Sheet 06 - Intro to Inference (Sampling Analysis)

##### Exercise 6.3
```{r, message=FALSE}
# Importing, getting a summary of population parameters and making boxplots
df <- read_csv("age_first_child.csv")
summary(df$age)
ggplot(df, aes(y = age)) + geom_boxplot()

# Point Estimate
pe <- mean(df$age)
pe
```


```{r, message=FALSE}
# Bootstrap (1000) resamples
boot_dit <- df %>%
  specify(response = age) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

# Simple Statistics
mean(boot_dit$stat)
sd(boot_dit$stat)
visualise(boot_dit)
```

```{r, message=FALSE}
# Getting Quantiles
q <- quantile(boot_dit$stat, probs = c(0.05, 0.95))
q

# Determining length
diff(q)
```

##### Exercise 6.3
```{r, message=FALSE}
# Create a sample data
sample_data <- data.frame(expense = c(rep("cover", 443), rep("not cover", 322)))
sample_data

# Bootstrap (1000) resamples
boot_sample_data <- sample_data %>%
                      specify(response = expense, success = "not cover") %>%
                      generate(reps = 1000, type = "bootstrap") %>% 
                      calculate(stat = "prop")
visualize(boot_sample_data)

# Standard Deviation
sd(boot_sample_data$stat)

```
#### Sheet 07


#### Sheet 08 - Hypothesis testing using Infer & Pvalue command for one and two proportion testing
```{r, message=FALSE}
# Hypothesis 
df <- data.frame(status = c(rep("nausea", 7), rep("no nausea", 3)))

null_dist <- df %>%
  specify(response = status, success = "nausea") %>%
  hypothesize(null = "point", p = 0.6) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "prop")
```

```{r, message=FALSE}
#### pnorm() used to get the pvalue of 1 & 2 proportion tests

# Pvalue One Proportion
pnorm(-1.08995, lower.tail = FALSE)

# Pvalue two Proportion (!) multiply by 2

pnorm(-0.96311, lower.tail = FALSE) * 2
```

```{r, message=FALSE}
# chi-squared test (fitness & independence) pvalue
pchisq(21.4406, df = 4, lower.tail=FALSE)

```


#### Sheet 09
```{r}
# Confidence Intervals {90%=1.645} {95%=1.645} {98%=2.326} {99%=2.576}
# t-test

## Critical value 
p <- 1-(2.326/2)
qt(p, df=22)

```

#### Sheet 10
#### Sheet 11
#### Sheet 12
#### Sheet 13
#### Sheet 14