---
title: "Sheet 9"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Proble H.9.1
#### Dependencies
```{r, message=FALSE}
library(tidyverse)
library(openintro)
```
#### Data
```{r}
anes <- as.table(rbind(c(44, 29, 62, 36), c(77, 54, 131, 67)))
dimnames(anes) <- list(direction = c('right_direction', 'wrong_track'), 
                       region = c('north_central', 'northeast', 'south', 'west'))
addmargins(anes)
```

#### a) Evalue whether the ANES sample is representative of the population distribution of US residents:  

__Hypotheses:__  

  $H_{0}:$ Sample is representatie of the targeted population.  
  
  $H_{A}:$ Sample is not representatie of the targeted population.

__Conditions:__  

  __1.__ Independence Condition fullfilment once it is a random sample.  
  
  __2.__ Sample Size Condition: $ExpectedCases \ge 5$  
  
```{r}
sample <- 500
probabilities <- c(0.22, 0.18, 0.37, 0.23)
distribution <- sample * probabilities 
all_expected_cases <- matrix(distribution, nrow = 1, ncol=4)
all_expected_cases
```

Based on the tables with the expected values above, one can say that the Sample Size condition is also fullfilled!

  __3.__ Degree of Freedom Condition fullfilment: $df = k - 1 = 4 - 1 = 3$  
  
__T-test and p-value__
```{r}
# Using probabilities defined aboved
sums <- c(121, 83, 193, 103)
chisq.test(x = sums, p = probabilities)

```

__Conclusion:__  
$H_{0}$ can not be rejected, because p-value is sufficiently large $p-value = 0.3557 > 0.05$, which implies weak evidence against the null hypothesis, we fail to reject the null hypothesis and tthe sample is representative of the target population.

#### b) Region and direction

  __(i)__  
  __Response__ variable: Direction  
  
  __Explanatory__ variable: Region  
         
  __(ii)__  
  
  $H_{0}:$ Direction and region are independent. The direction does not vary by region.  
  
  $H_{A}:$ Direction and region are dependent. The direction varies by region.

  __(iii)__  __T-test and p-value__
```{r}
chisq.test(anes)
```

## Proble H.9.2

#### a) __Hypotheses:__  

  $H_{0}:$ The urban police officers have the same average lead exposure than the suburb individuals  
  
  $H_{A}:$ The urban police officers have a different average lead exposure than the suburb individuals  
  
#### b) __Conditions:__  

__1__ Independence: There is no evidence that the sample is randomnized, and therefore this condition isn't fullfilled.  
__2__ Normality Thumb-Rule: $n \ge 30: n = 52$ implies no information about extreme outliers, so we assume sampling distribution is nearly normal.  

#### c)
```{r}
difference <- 124.32 - 35
difference
null <- 0
null
standard_error <- 37.74/sqrt(52)
standard_error
df <- 52 - 1
df
t <- (difference - null)/standard_error
t
p_value <- pt(t, df=df, lower.tail = F) * 2 # I have multiplied the p-value by 2, once it is a two-sided hypothesis

p_value
```

Based on $p-value = 9.913949e-23$ one can conclude: the data shows evidence that lead exposure of the urban police officers is different than the lead of thesuburb police officers.
