---
title: "Sheet07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Necessary Packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(infer)
```

## a) Creating a dataframe
```{r}
nearsightedness <- c(rep("yes", 21), rep("no", 194-21))
df <- data.frame(nearsightedness)
as_tibble(df)
```

## b) Runnning the command
```{r}
table(df)
```

## c) Null and Alternative Hypothesis

_Null Hypothesis:_ Nearsightness affect 8% of the childreen. In other words, the data provides no evidence about the inaccuracy of the 8% value.The data differ from the 8% value due to chance.  $$ H_{0}: μ_{x} = 8\%$$

_Alternative Hypothesis:_ Nearsightness affect more then 8% of the childreen. In other words, the data provides evidence that the 8% is inaccurate.The data doesn’t differ from the 8% value due to chance. $$ H_{a}: μ_{x} > 8\%$$


## d) Null Distributions based on 1000 resamples
```{r, message=FALSE, warning=FALSE}
set.seed(12345)
null_distn <- df %>%
  specify(response = nearsightedness, success = "yes") %>%
  hypothesize(null = "point", p = 0.08) %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop") 
null_distn
```

## e) Testing Null Hypothesis (from exercise (c))
```{r}
p_value <- null_distn %>%
  get_pvalue(obs_stat = 21/194, direction = "greater")
p_value

null_distn %>%
  visualize() +
  shade_p_value(obs_stat = 21/194, direction = "greater")

significance_level <- 0.05
```

## f) Conclusion

If the p-value is less than or equal to the significance level, the null hypothesis is rejected.
```{r}
p_value <= significance_level
```

Since the statement above does not hold, one must say that there is NOT sufficient evidence to reject the Null Hypothesis.Going back to the question: `Do these data provide evidence that the 8% value is inaccurate?` We can not exclude, that the data doesn’t provide any evidence about the inaccuracy of the 8% value. Our observed data might differ due to chance. This means, we have no evidence whether the statement `It is believed that near-sightedness affects about 8% of all children.` is inaccurate.
