---
title: "Solution to H.3.2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading necessary packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

## a) Read in the data "RKI_COVID19_200504.csv"
```{r}
covid_data <- read_csv(file = "data_for_homework/RKI_COVID19_200504.csv")
covid_data
```

## b) Infected per day

__(Step 1)__: Creating a infected_per_day data frame
```{r}
infected_per_day <- (
  covid_data %>%
    select(number_infected, date) %>%
    group_by(date) %>%
    summarize(num = sum(number_infected))
)
infected_per_day
```

__(Step 2)__: Using the function geom_line() to create a line plot of the total number of
infected per day against date

```{r}
ggplot(infected_per_day, aes(x=date, y=num)) +
    geom_line() + labs(title="Number of infected people per day")
```

## c) Federal State

__(Step 1)__: Grouping original data by `federal_state` and computing the average number of infected per state
```{r}
state_data <- (
  covid_data %>%
    group_by(federal_state, date) %>%
    summarize(infected_per_day = sum(number_infected))
)

state_data %>%
  summarize(avg_infected_per_state = mean(infected_per_day))
```

## d) Bavaria Analysis

__(Step 1)__: Filtering state data according to "Bayern" and applying the following analysis:

  * Mean
  * Median
  * Standard deviation
  * Maximum
  * Total Number
  
```{r}
bavaria_data <- (
  covid_data %>%
    filter(federal_state == "Bayern") %>%
    group_by(date) %>%
    summarise(number_of_infected = sum(number_infected)) %>%
    summarize(mean = mean(number_of_infected), median = median(number_of_infected), sd = sd(number_of_infected), 
              max = max(number_of_infected), total = sum(number_of_infected))
)
bavaria_data
```
  

## e) Contigency Table

__(Step 1)__: Read in the new data "RKI_COVID19_200504_table.csv"

```{r}
covid_table_data <- read_csv(file = "data_for_homework/RKI_COVID19_200504_table.csv")
covid_table_data
```

__(Step 2)__: Computing a contingency table for the variables `sex` and `age_group`
```{r}
contigency_table <- addmargins(table(covid_table_data$sex, covid_table_data$age_group))
contigency_table
```

__Description__: 

The dataset used is "RKI_COVID19_200504_table.csv". The table displayed above consists of observations of infected people in Germany ordered by two categorical variables: `sex` and `age_group`. 

Margins are added to help in the explanation of the table. The rows are depicted by categories of sex: `M` for men, `W` for women, and `Sum` for the sum of men and women under a respective age group. The columns are depicted by categories of age (all in Year units): `A00-A04`, `A05-A14`, `A15-A34`, `A35-A59`, `A60-A79`, `A80+` and `Sum` for sum of all cases of men and women.

The total of observations are 162524 cases. Out of those 77475 are male while 85049 are female. Most infected observations are within age category `A35-A59`, respectively 68258 cases. `A00-A04` group is the one with least infected cases, respectively 1420 cases.

`M` and `W` infections oscillates according to age groups. On the one hand, under ages,`A00-A04`,`A05-A14`, and `A60-A79`, male infection cases are bigger than female cases. On the other hand, under ages, `A15-A34`, `A35-A59`,and `A80+`, female infection cases are bigger than male ones. In the next exercise, the same table is extended to frequency and percentage values.  

## f) Probability

__(Step 1)__: Using the contigency table to get the frequencies / "percentages" table

```{r}
frequency_table <- addmargins(prop.table(table(covid_table_data$sex, covid_table_data$age_group)))
frequency_table
```

__(Step 2)__: Considering all observations are infected, as the exercise states. We can read from the table above the probability that an infected person is a male `and` between 60 and 79 years old.

$$\mathrm{P}(Male \land Age_{60-79})$$
```{r}
probability <- frequency_table["M","A60-A79"]
probability 
```

We can multiply `probability` by `100` to get the value in percentages
```{r}
answer <- probability * 100 
cat(answer,"%")
```

__Answer__: The probability that an infected person is $\mathrm{P}(Male \land Age_{60-79})$ is equal to 10.01329 %.